\begin{thebibliography}{0}

  \bibitem{EuropeanParliamentReportOnCyberDefence}
    Paet, U. (25/05/2018). European Parliament: REPORT on cyber defence.
    \url{http://www.europarl.europa.eu/doceo/document/A-8-2018-0189_EN.pdf?redirect}

  \bibitem{EuropeanParliamentDesignatingAsDangerous}
    Annemans, G. (13/06/2018). European Parliament: Designating programmes and companies as 'dangerous' from the point of view of cyber
defence
    \url{http://www.europarl.europa.eu/doceo/document/P-8-2019-001206_EN.pdf}

  \bibitem{Kaspersky2020EulaEn}
    Lab., K. (2019). Kaspersky Lab. Retrieved from Kaspersky Lab.
    \url{https://products.s.kaspersky-labs.com/homeuser/kav2020/20.0.14.1085abc/english-INT-0.2007.0/3231373433327c44454c7c4e554c4c/eula_en.txt}

  \bibitem{McAfeeEnterpriseEulaEnGb}
    McAfee (April, 2018). McAfee. Retrieved from McAfee.
    \url{https://www.mcafee.com/enterprise/en-us/assets/legal/end-user-license-agreements-en-gb.pdf}

  \bibitem{MalwarebytesEula}
    Malwarebytes (2020). Malwarebytes. Retrieved from Malwarebytes:
    \url{https://www.malwarebytes.com/eula/}

  \bibitem{KasperskyBoundariesOfTrust}
    Lab., K. (2019). Kaspersky Lab. Retrieved from Kaspersky Lab. blog:
    \url{https://www.kaspersky.com/blog/the-boundaries-of-trust/}

  \bibitem{ThreatHuntingForDummies}
    Threat Hunting For Dummies® Carbon Black Special Edition. Peter H. Gregory

  \bibitem{ProactiveHunting}
    PROACTIVE HUNTING The Last Line of Defense Against the “Mega Breach”

  \bibitem{HardwareMalware}
    Hardware malware. [S.l.]: Morgan & Claypool. ISBN 9781627052528.

  \bibitem{ContextBasedMalware}
    Analysis and classification of context-based malware behavior. Mohammadhadi Alaeiyan, Saeed Parsa, Mauro Conti

  \bibitem{LearningFromContext}
    Learning from Context: Exploiting and Interpreting File Path Information for Better Malware Detection. Adarsh Kyadige, Ethan M. Rudd, Konstantin Berlin

  \bibitem{SoftwareEngineering}
    Richard F. Schmidt, in Software Engineering, 2013

  \bibitem{ResidentViruses}
    Sharma, S (2013). "Terminate and Stay Resident Viruses" (PDF). International Journal of Research in Information Technology. 1 (11): 201–210.

  \bibitem{FilelessAttacks}
    "Fileless attacks against enterprise networks". Secure List. Secure List. Retrieved 20 February 2017.

  \bibitem{AdvacedVolatileThreat}
    "Advanced volatile threat: New name for old malware technique?". CSO. CSO. Retrieved 20 February 2017.

  \bibitem{MicrosoftPecoff}
    Microsoft Portable Executable and Common Object File Format Specification. Revision 6.0 February 1999. Microsoft Corporation.

  \bibitem{DynamicLinkLibraries}
    Corporation, M. (31/05/2018) Microsoft Corporation. Retrieved from Microsoft Docs.
    \url{https://docs.microsoft.com/es-es/windows/win32/dlls/dynamic-link-libraries?redirectedfrom=MSDN}

  \bibitem{Nist2013}
    NIST (April, 2013). Rebecca M. Blank and Patrick D. Gallagher. Security and Privacy Controls for Federal Information Systems and Organizations. Retrieved from NIST.
    \url{https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-53r4.pdf}

  \bibitem{Rfc4949}
    RFC (August, 2007). R. Shirey. Obtained from Internet Engineering Task Force.
    \url{https://tools.ietf.org/html/rfc4949}

  \bibitem{NistGlossary2020}
    NIST (2020). NIST. Retrieved from NIST glossary.
    \url{https://csrc.nist.gov/glossary/term/malware}

  \bibitem{LayeredDetectionMethod}
    A Layered Detection Method for Malware Identification. Ting Liu, Xiaohong Guan, Yu Qu, Yanan Sun

  \bibitem{RussianStoleNsaSpySecrets}
    Lubold, Gordon; Harris, Shane (6 October 2017). "Russian Hackers Stole NSA Spy Secrets". The Wall Street Journal. New York City. pp. 1, 4. Retrieved 12 October 2017

  \bibitem{KasperskyToolForSpying}
    Harris, Shane; Lubold, Gordon (2017-10-11). "Russia Has Turned Kaspersky Software Into Tool for Spying". Wall Street Journal. ISSN 0099-9660. Retrieved 2017-10-19.

  \bibitem{KasperskyTransparencyCenter}
    Lab., K. (2020). Kaspersky Lab. Retrieved from Kaspersky Lab.
    \url{https://www.kaspersky.com/transparency-center}

  \bibitem{EugeneKasperskyBlog2017}
    Kaspersky, E. (30/06/2017). Eugene Kaspersky. Retrieved from Eugene Kaspersky blog.
    \url{https://eugene.kaspersky.com/2017/06/30/keeping-cybersecurity-separate-from-geopolitics/}

  \bibitem{McAfeeEnterpriseEula2019}
    McAfee (June, 2019). McAfee. Retrieved from McAfee.
    \url{https://www.mcafee.com/enterprise/en-us/assets/legal/end-user-license-agreements-en-us.pdf}

  \bibitem{KaitaiStructDoc}
    Struct, K. (2020). Kaitai Struct. Retrieved from Kaitai Struct documentation.
    \url{https://doc.kaitai.io/}

  \bibitem{MalwarebytesUserGuide}
    Malwarebytes for Windows User Guide. Version 3.6.1. 19 September 2018. Copyright © 2018 Malwarebytes. All rights reserved.

  \bibitem{AmazonS3RestApi}
    Amazon (2020). Amazon Web Services, Inc. Retrieved from Amazon S3 documentation.
    \url{https://docs.aws.amazon.com/es_es/AmazonS3/latest/dev/RESTAPI.html}

  \bibitem{MalwarebytesPremium}
    Malwarebytes (2020). Malwarebytes. Retrieved from Malwarebytes.
    \url{https://es.malwarebytes.com/premium/}

  \bibitem{ZeltserShareMalware}
    Zeltser, L. (24/03/2018) Lenny Zeltser. Retrieved from Lenny Zeltser.
    \url{https://zeltser.com/share-malware-with-researchers/}

  \bibitem{MicrosoftDefenderAtp2020}
    Corporation, M. (01/14/2020) Microsoft Corporation. Retrieved from Microsoft Docs.
    \url{https://docs.microsoft.com/en-us/windows/security/threat-protection/microsoft-defender-atp/advanced-hunting-schema-reference}

  \bibitem{CarbonBlack2017}
    CarbonBlack (April, 2017). CarbonBlack. Retrieved from CarbonBlack.
    \url{https://www.carbonblack.com/wp-content/uploads/2017/04/BanHash-B.png}

  \bibitem{MicrosoftRdpCrashes2019}
    Corporation, M. (07/11/2019) Microsoft Corporation. Retrieved from Microsoft blog site.
    \url{https://www.microsoft.com/security/blog/2019/11/07/the-new-cve-2019-0708-rdp-exploit-attacks-explained/}

  \bibitem{VirusTotalFileSearch2020}
    VirusTotal (2020). VirusTotal. Retrieved from VirusTotal file search:
\url{https://www.virustotal.com/intelligence/help/file-search/}

  \bibitem{IntrusionDetectionNetworks}
    Intrusion Detection Networks: A Key to Collaborative Security. Carol Fung, Raouf Boutaba

  \bibitem{AVComparatives2020}
    AV-Comparatives (2020). AV-Comparatives. Retrieved from AV-Comparatives:
    \url{https://www.av-comparatives.org/}

  \bibitem{AVTest}
    AV-Test (2020). AV-Test. Retrieved from AV-Test.
    \url{https://www.av-test.org/}

  \bibitem{AVComparativesResults2019}
    AV-Comparatives (July, 2019). AV-Comparatives. Retrieved from AV-Comparatives.
    \url{https://www.av-comparatives.org/tests/business-security-test-2019-march-june/}

  \bibitem{VXVault2020}
    VXVault (2020). VXVault. Retrieved from VXVault.
    \url{http://vxvault.net/ViriList.php}

  \bibitem{VirusTotalUpload2020}
    VirusTotal (2020). VirusBay. Retrieved from VirusTotal.
    \url{https://www.virustotal.com/gui/home/upload}

  \bibitem{MalShare2020}
    MalShare (2020). MalShare. Retrieved from MalShare.
    \url{https://malshare.com/}

  \bibitem{VirusShare2020}
    VirusShare (2020). VirusShare. Retrieved from VirusShare.
    \url{https://virusshare.com/}

  \bibitem{VirusBay2020}
    VirusBay (2020). VirusBay. Retrieved from VirusBay.
    \url{https://beta.virusbay.io/sample/browse}

  \bibitem{VirusTotalTermsOfService2020}
    VirusTotal (2020). VirusTotal. Retrieved from VirusTotal Terms of Service.
    \url{https://support.virustotal.com/hc/en-us/articles/115002145529-Terms-of-Service}

  \bibitem{NistGlossaryFirmware2020}
    NIST (2020). NIST. Retrieved from NIST glossary.
    \url{https://csrc.nist.gov/glossary/term/firmware}

  \bibitem{AuthenticatedEncryption2000}
    Bellare M., Namprempre C. (2000) Authenticated Encryption: Relations among Notions and Analysis of the Generic Composition Paradigm. In: Okamoto T. (eds) Advances in Cryptology — ASIACRYPT 2000. ASIACRYPT 2000. Lecture Notes in Computer Science, vol 1976. Springer, Berlin, Heidelberg

  \bibitem{Eurocrypt2002}
    Serge Vaudenay (2002). Security Flaws Induced by CBC Padding Applications to SSL, IPSEC, WTLS... EUROCRYPT 2002.

  \bibitem{Oaep}
    Manger, James. "A Chosen Ciphertext Attack on RSA Optimal Asymmetric Encryption Padding (OAEP) as Standardized in PKCS #1 v2.0". Telstra Research Laboratories.

  \bibitem{AuthenticatedEncryption2013}
    "Information technology -- Security techniques -- Authenticated encryption". 19772:2009. ISO/IEC. Retrieved March 12, 2013.

  \bibitem{CanonicalProjectStructure}
    Canonical Project Structure. Boris Kolpackov 2018-10-08

  \bibitem{ClamAV}
    ClamAV (2020). ClamAV. Retrieved from ClamAV Github site.
    \url{https://github.com/Cisco-Talos/clamav-devel}

  \bibitem{BBCMarcinKleczynski}
    BBC (22/07/2019). Joe Tidy. Retrieved from BBC News.
    \url{https://www.bbc.com/news/business-49015609}


\end{thebibliography}